---
title: "Working Title"
author: "Kiwi & Isabella"
format: revealjs
embed-resources: true
html-math-method: mathml
execute: 
  warning: false
  echo: false
  error: false
---

```{r}
#| label: setup
#| include: false

library(tidyverse)
library(mosaic)
```

<!-- Please note that this is not the final format for the presentation, just for the submission of Part 1 of the Project.  See the Project Presentation Template for a more complete version of the presentation slide requirements (but still read through the OVERVIEW) -->

<!--- Note: you will want to replace my instructions with your actual responses on each slide --->


## Research Question(s)

Write your research question(s) on this slide
> Is there a significant difference in population means of mean GO reaction time (s) in casual super smash bro gamers and in top 150 super smash bro gamers? 

## Description of Data

```{r}
gamer <- read_csv("Esports_Study_Data.csv")
nerds <- gamer |> 
  filter(Game %in% c("Casual-SB", "Elite-SB"))
```


- Identify Population, Individuals, Sample
> Population: All super smash bros ultimate players that have competed in the Monterey and San Jose Counties  
Case: smash bros ultimate player that has competed in the Monterey or San Jose Counties   
Sample : 43 super smash bros ultimate players that have competed in the Monterey and San Jose Counties

- Identify Variables and Types, including new variables you will create
<<<<<<< HEAD
>Health and Lifestyle:  
 Sex - Male or Female (Qualitative)  
 Age_years (Quantitative)  
 Gaming_hr_week_ratio - Hours per week gaming (Quantitative)  
 Caffeine_Intake_mg_d - Reported caffeine intake (mg) per day (Quantitative)  
 Sleep_hrs - Typical hours of sleep per night (Quantitative)  
 Exercise_hours_week - Hours per week exercising (Quantitative)  
Difference (Actual mean - Practice mean) of Cognitive measure test in milliseconds (ms):  
 SR_ROC_Mean_RT - Simple Reaction test (Quantitative)  
 ROC_Mean_Go_RT - Go/No Go test (Quantitative)  
 ROC_Mean_Valid_Cue_RT_ms - Posner Cueing test (valid cue) (Quantitative)  
 PP_ROC_Building_Test - Purdue Pegboard test (Quantitative)  
Level of Gaming/Type:  
 Gaming (measured as Non-Gamer, Casual-SB, Elite-SB, FPS, MOBA) (Qualitative)  
=======
>Health and Lifestyle: 
 Sex - Male or Female (Qualitative)
 Age_years (Quantitative)
 Gaming_hr_week_ratio - Hours per week gaming (Quantitative)
 Caffeine_Intake_mg_d - Reported caffeine intake (mg) per day (Quantitative)
 Sleep_hrs - Typical hours of sleep per night (Quantitative)
 Exercise_hours_week - Hours per week exercising (Quantitative)
Difference (Actual mean - Practice mean) of Cognitive measure test in milliseconds (ms):
 SR_ROC_Mean_RT - Simple Reaction test (Quantitative)
 ROC_Mean_Go_RT - Go/No Go test (Quantitative)
 ROC_Mean_Valid_Cue_RT_ms - Posner Cueing test (valid cue) (Quantitative)
 PP_ROC_Building_Test - Purdue Pegboard test (Quantitative)
Level of Gaming/Type:
 Gaming (measured as Non-Gamer, Casual-SB, Elite-SB, FPS, MOBA) (Qualitative)
>>>>>>> dee06a76a177a40dfbd0295d0fc6b101dbbe56d1
 Abbreviations: SB (Super Smash Bros Ultimate), FPS (First Person Shooter), MOBA (multiplayer online battle arena)

- Describe how data was collected
> The participant collection included visiting local Monterey, San Jose, and CSUMB tournaments for esports, visiting the CSUMB library to ask people to join, and other non-random methods of obtaining participants.

## Summary Statistics and Graphics
Provide descriptions and inset values from R output.
```{r}
nerds |> 
  filter(Game %in% "Casual-SB")|>
  gf_histogram(~Actual_Mean_Go_RT_ms)

nerds |> 
  filter(Game %in% "Elite-SB")|>
  gf_histogram(~Actual_Mean_Go_RT_ms)

nerds|>
    df_stats(Actual_Mean_Go_RT_ms~Game)
```


## Analysis
Provide analysis using parametric methods (will not be in your final presentation)

```{r}
t.test(Actual_Mean_Go_RT_ms~Game, data = nerds, alternative = "less")
```

## Failure of Parametric Methods
Describe why or provide evidence for why parametric methods are not reasonable
> Parmetric methods are not reasonable for assessment do to the right skew that we see in both of the two groups for our response variable. The skew and the small sample size make parametric methods innappropriate to use for analysis.

