---
title: "Working Title"
author: "Kiwi & Isabella"
format: revealjs
embed-resources: true
html-math-method: mathml
execute: 
  warning: false
  echo: false
  error: false
---

```{r}
#| label: setup
#| include: false

library(tidyverse)
```

<!-- Please note that this is not the final format for the presentation, just for the submission of Part 1 of the Project.  See the Project Presentation Template for a more complete version of the presentation slide requirements (but still read through the OVERVIEW) -->

<!--- Note: you will want to replace my instructions with your actual responses on each slide --->


## Research Question(s)

Write your research question(s) on this slide
> Is there a significant population shift in mean GO reaction time (s) between casual super smash bro gamers and top 150 super smash bro gamers? 

## Description of Data

- Identify Population, Individuals, Sample
> Population: All super smash bros ultimate players that have competed in the Monterey and San Jose Counties  
Case: smash bros ultimate player that has competed in the Monterey or San Jose Counties   
Sample : 43 super smash bros ultimate players that have competed in the Monterey and San Jose Counties

- Identify Variables and Types, including new variables you will create
>Health and Lifestyle: 
 Sex - Male or Female (Qualitative)
 Age_years (Quantitative)
 Gaming_hr_week_ratio - Hours per week gaming (Quantitative)
 Caffeine_Intake_mg_d - Reported caffeine intake (mg) per day (Quantitative)
 Sleep_hrs - Typical hours of sleep per night (Quantitative)
 Exercise_hours_week - Hours per week exercising (Quantitative)
Difference (Actual mean - Practice mean) of Cognitive measure test in milliseconds (ms):
 SR_ROC_Mean_RT - Simple Reaction test (Quantitative)
 ROC_Mean_Go_RT - Go/No Go test (Quantitative)
 ROC_Mean_Valid_Cue_RT_ms - Posner Cueing test (valid cue) (Quantitative)
 PP_ROC_Building_Test - Purdue Pegboard test (Quantitative)
Level of Gaming/Type:
 Gaming (measured as Non-Gamer, Casual-SB, Elite-SB, FPS, MOBA) (Qualitative)
 Abbreviations: SB (Super Smash Bros Ultimate), FPS (First Person Shooter), MOBA (multiplayer
online battle arena)

- Describe how data was collected
> The participant collection included visiting local Monterey, San Jose, and CSUMB tournaments for esports, visiting the CSUMB library to ask people to join, and other non-random methods of obtaining participants.

## Summary Statistics and Graphics
Provide descriptions and inset values from R output.


## Analysis
Provide analysis using parametric methods (will not be in your final presentation)
```{r}
#analysis code
```

## Failure of Parametric Methods
Describe why or provide evidence for why parametric methods are not reasonable

